Notes

### 2022-09-05 chapters/abstract.tex
Replace cover and minor adjustments

In this thesis we propose a novel Bayesian approach for functional linear and logistic regression models, based on the theory of reproducing kernel Hilbert spaces (RKHS's). These recently-proposed models build upon the RKHS associated with the covariance function of the underlying stochastic process, and can be viewed as a finite-dimensional approximation to the classical functional regression paradigm. The corresponding functional model (or the functional logistic equation in the case of binary response) is determined by a function living on a dense subspace of the RKHS of interest, which has a tractable parametric form. By imposing a suitable prior distribution on this space, we can perform data-driven inference via standard Bayes methodology. The posterior distribution can be estimated through Markov chain Monte Carlo methods, which do not require a complete specification of the posterior density.

>>>>

In this thesis we propose a novel Bayesian approach for functional linear and logistic regression models based on the theory of reproducing kernel Hilbert spaces (RKHS's). These recently-proposed models build upon the RKHS associated with the covariance function of the underlying stochastic process, and can be viewed as a finite-dimensional approximation to the classical functional regression paradigm. The corresponding functional model (or the functional logistic equation in the case of binary response) is determined by a function living on a dense subspace of the RKHS of interest, which has a tractable parametric form. By imposing a suitable prior distribution on this space, we can perform data-driven inference via standard Bayes methodology. The posterior distribution can be estimated through Markov chain Monte Carlo methods, which do not require a complete specification of the posterior density.

### 2022-09-05 chapters/background-related-work.tex
Replace cover and minor adjustments

Turning our attention to logistic regression, a similar \(L^2\)-based functional logistic equation can be derived for the binary classification problem via the logistic function:
\begin{equation}\label{eq:l2-logistic-model}
  \P(Y=1 \mid X) = \frac{1}{1 + \exp\{-\alpha_0 - \dotprod{X}{\beta}\}},
\end{equation}
where \(\alpha_0 \in \R\) and \(\beta \in L^2[0, 1]\). In this situation, the most common way of estimating the slope function \(\beta\) is via its Maximum Likelihood Estimator (MLE). However, not only do the same complications as in the linear regression model apply in this situation, but there is also the additional problem that in functional settings the MLE does not exist with probability one under fairly general conditions \citep[see][Sec.~3.2]{berrendero2018functional}.

>>>>

Turning our attention to logistic regression, a similar \(L^2\)-based functional logistic equation can be derived for the binary classification problem via the logistic function:
\begin{equation}\label{eq:l2-logistic-model}
  \P(Y=1 \mid X) = \frac{1}{1 + \exp\{-\alpha_0 - \dotprod{X}{\beta}\}},
\end{equation}
where \(\alpha_0 \in \R\) and \(\beta \in L^2[0, 1]\). In this situation, the most common way of estimating the slope function \(\beta\) is via its Maximum Likelihood Estimator (MLE). However, not only do the same complications as in the linear regression model apply in this situation, but there is also the additional problem that in functional settings the MLE does not exist with probability one under fairly general conditions \citep[see][]{berrendero2018functional}.

### 2022-09-05 chapters/bayesian-functional-regression.tex
Replace cover and minor adjustments

In the case of functional logistic regression, we can regard the binary response variable \(Y\in\{0, 1\}\) as a Bernoulli random variable given \(X=x \in L^2[0, 1]\), and as usual suppose that \(\log\left(p(x)/(1-p(x))\right)\) is linear in \(x\), where \(p(x)=\P(Y=1| X=x)\). Then, following the approach  suggested by \citet{berrendero2018functional}, a RKHS model might be given, in terms of the isometric transformation \(X \mapsto \dotprod{X}{\alpha}_K = \Psi_X(\alpha)\), by the equation
\begin{equation}\label{eq:rkhs-model-logistic}
  \P(Y=1 \mid X) = \frac{1}{1 + \exp\{-\alpha_0 - \dotprod{X}{\alpha}_K\}}, \quad \alpha_0 \in \R, \ \alpha \in \Hcal_{0,p}(K).
\end{equation}

>>>>

In the case of functional logistic regression, we can regard the binary response variable \(Y\in\{0, 1\}\) as a Bernoulli random variable given \(X=x \in L^2[0, 1]\), and as usual suppose that \(\log\left(p(x)/(1-p(x))\right)\) is linear in \(x\), where \(p(x)=\P(Y=1| X=x)\). Then, following the approach  suggested by \citet{berrendero2018functional}, a RKHS model might be given, in terms of the correspondence \(\dotprod{X}{\alpha}_K = \Psi_X(\alpha)\), by the equation
\begin{equation}\label{eq:rkhs-model-logistic}
  \P(Y=1 \mid X) = \frac{1}{1 + \exp\{-\alpha_0 - \dotprod{X}{\alpha}_K\}}, \quad \alpha_0 \in \R, \ \alpha \in \Hcal_{0,p}(K).
\end{equation}
